%!TEX root=../main.tex

% German abstract
\begin{abstract}[ngerman]
Für viele Schülerinnen und Schüler zählen die vielen Exkursionen, Sportwochen, Sprachreisen, Skikurse und Projektwochen zu den schönsten Erinnerungen ihrer Schullaufbahn. Momentan sind diese jedoch noch mit viel Bürokratie hier am TGM verbunden. Für Exkursionen müssen diverse Anträge ausgefüllt und Reisekostenabrechnungen durchgeführt werden. Dies führt zu einer Mehrbelastung der Lehrkräfte. \textit{Refundable} soll den Lehrern die einfache Verwaltung ihrer Exkursionen ermöglichen, sodass eine Mehrbelastung auf ein Minimum reduziert werden kann. Durch automatische Generation und Verwaltung verschiedener Anträge und Daten übernimmt und vereinfacht \textit{Refundable} die sonst notwendige Bürokratie. Das Ziel von \textit{Refundable} ist es den Fokus weg von der Bürokratie auf die eigentliche Exkursion zu lenken.
\end{abstract}

% English abstract
\begin{abstract}[english]
For many teachers, the numerous excursions, sporting weeks, language and skiing trips as well as project weeks at the TGM are among the fondest moments of their school careers. Currently, these activities require considerable administrative work. Some of the necessary paperwork includes filling out numerous application forms and submitting travel expense reports, this can put additional unnecessary strain on teachers. \textit{Refundable} aims to provide teachers with a tool for easily managing their excursions and reduces the additional workload to a minimum. By automatically generating and managing various applications, the \textit{Refundable} software will eliminate much of the necessary paperwork. The aim of \textit{Refundable} is to shift the focus away from administrative tasks to allow teachers to focus on creating a memorable experience for all participants of a projekt week.
\end{abstract}